Statically Typed String Sanitation Inside a Python

### 2014-08-06 sanitation-psp14/sanitation-psp14-short.tex
Cleaned up safety/correctness divide

\begin{thm}{Safety and Sanitation Correctness for the String Fragment of P.} \label{thm:scorrect}
  Let $S$ be a term in the source language. If $\sctx \vdash S : \stringin{r}$ 
  then $S \sreduces \rstr{s}$, $\sctx \rstr{s} : \stringin{r}$, and $s \in \lang{r}$; or else $S \err$.
\end{thm}
\begin{proof}
By induction on the typing relation, where (a) case holds by lemma \ref{thm:regexprops} in the S-T-Concat case and lemma \ref{thm:substcorrespondence} in the S-T-Replace case..
The (b) cases hold by unstated, but standard, error propagation rules.
\end{proof}

@@

@@

\begin{thm}{Translation Correctness} \label{thm:tcorrect}
If $\sctx \vdash S : \stringin{r}$ then there exists a $P$ such that $\trden{S} = P$ and either: 
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, or
(b) $P \err$ and $S \err$.
\end{thm}

@@

\begin{thm}
If If $\sctx \vdash S : \stringin{r}$ and $\trden{S} = P$ then either:
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, or                      
(b) $P \err$ and $S \err$. 
\end{thm}
\begin{proof}
  The theorem  follows directly from canonical forms for translations and theorem \ref{thm:tcorrect}.
\end{proof}

>>>>

\begin{thm}{Safety and Sanitation Correctness for the String Fragment of P.} \label{thm:scorrect}
  Let $S$ be a term in the source language. If $\sctx \vdash S : \stringin{r}$ 
  then $S \sreduces \rstr{s}$ and $\sctx \vdash \rstr{s} : \stringin{r}$; or else $S \err$.
\end{thm}
\begin{proof}
By induction on the typing relation, where (a) case holds by lemma \ref{thm:regexprops} in the S-T-Concat case and lemma \ref{thm:substcorrespondence} in the S-T-Replace case..
The (b) cases hold by unstated, but standard, error propagation rules.
\end{proof}

@@

\begin{thm}{Correctness of Input SAnitation for $\lambdas$.}\label{thm:scorrect}
  If  $\sctx \vdash S : \stringin{r}$ and $S \sreduces \rstr{s}$ then $s \in \lang{r}$.
\end{thm}
\begin{proof}
  Follows directly from type safety, canonical forms for $\lambdas$.
\end{proof}

@@

\begin{thm}{Translation Correctness.} \label{thm:tcorrect}
If $\sctx \vdash S : \stringin{r}$ then there exists a $P$ such that $\trden{S} = P$ and either: 
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, or
(b) $P \err$ and $S \err$.
\end{thm}

@@
